Exploratory Analysis Script

### 2024-03-22 code/eda-code/eda-v1.qmd
Debugged code
After Erick's peer feedback

```{r}
# Create dummy variables
# Combine "Preta" and "Parda" into a new category Afro or EuroDescent and create dummy variable
ML_summary$ModifiedColor <- ifelse(ML_summary$Color == "Branca", "EuroDescent",
  ifelse(ML_summary$Color == "Preta", "AfroDescent",
  ifelse(ML_summary$Color == "Parda", "AfroDescent", NA)))

# Or using recode factor from dplyr (easier)
# ML_summary$ModifiedColor <- recode_factor(ML_summary$Color, "Parda" = "AfroDescent", "Preta" # = "AfroDescent", "Branca" = "EuroDescent")

@@

```{r}
# Create dummy variables
# Combine "Preta" and "Parda" into a new category Afro or EuroDescent and create dummy variable
ML_linear$ModifiedColor <- ifelse(ML_linear$Color == "Branca", "EuroDescent",
  ifelse(ML_linear$Color == "Preta", "AfroDescent",
  ifelse(ML_linear$Color == "Parda", "AfroDescent", NA)))

# Or using recode factor from dplyr (easier)
# ML_linear$ModifiedColor <- recode_factor(ML_linear$Color, "Parda" = "AfroDescent", "Preta" # = "AfroDescent", "Branca" = "EuroDescent")

>>>>

```{r}
# Create dummy variables

# Or using recode factor from dplyr (easier)
ML_summary$ModifiedColor <- recode_factor(ML_summary$Color, "Parda" = "AfroDescent", "Preta" = "AfroDescent", "Branca" = "EuroDescent")

@@

```{r}
# Create dummy variables
# Create dummy variables using recode factor from dplyr
 ML_linear$ModifiedColor <- recode_factor(ML_linear$Color, "Parda" = "AfroDescent", "Preta" = "AfroDescent", "Branca" = "EuroDescent")
